### 2011-01-27 paper/fitnessEvaluation.tex

\editbox{proofread.}

@@

>>>>

\edit{Put this in there somewhere:}

To be as fair as possible when obtaining the results presented in
\secref{results}, we picked three random points --- $\vec{\theta}_A$,
$\vec{\theta}_B$, and $\vec{\theta}_C$ --- and started all seven
methods at these points...

\editbox{proofread. especially middle paragraph}

@@

The size of the Wii remote window is approximately 69 x 47 cm. A
concern about this is that if the robot walks further than usual,
it walks outside the viewable range and thus does not count the run.
This possibility could bias the final results reported on the robot.
% probably could be better written
